---
title: "Text: Words 2"
author: "Quinn Johnston"
editor: visual
format:
  html:
    embed-resources: true
    code-fold: true  # new
execute:
  echo: true
  message: false
  warning: false
---

```{r setup}
library(tidyverse)
library(rvest)
library(wordcloud)
library(tm)
library(tidytext)
library(SnowballC)
```

# Romeo and Juliet

"Oh Romeo, Romeo, wherefore art thou Romeo?"

Full script - <http://shakespeare.mit.edu/romeo_juliet/full.html>

Let's explore...

1.  Whose name appears more often, Romeo or Juliet?
2.  Perform "pre-cleaning" on the file to remove extraneous characters.
3.  Identify which word appears most often in the text

# Read in Romeo and Juliet

### Option 1 - from file

```{r}
RandJ0 <- read_file("Romeo and Juliet Entire Play.txt")
str(RandJ0)
```

### Option 2 - directly

```{r}
"http://shakespeare.mit.edu/romeo_juliet/full.html" |> 
  read_html() |> 
  html_text2() |> 
  str_sub(1,500)
```

# Term Frequency

Whose name appears more often, Romeo or Juliet?

```{r}
# convert the raw Romeo & Juliet text into a data frame
RandJ_df <- tibble(text = RandJ0)

# tokenize the text into individual words (lowercases & removes punctuation)
RandJ_words <- RandJ_df |>
  unnest_tokens(word, text)

# term frequency (before any additional cleaning)
tf_raw <- RandJ_words |>
  count(word, sort = TRUE)

# display the 20 most frequent words
tf_raw |> slice(1:20)

# compare how often the names "romeo" & "juliet" appear
tf_raw |> filter(word %in% c("romeo", "juliet"))
```

# Pre-cleaning / Tokenize

Perform "pre-cleaning" on the file to remove extraneous characters.

```{r}
# remove empty tokens & any tokens containing digits
RandJ_clean <- RandJ_words |>
  filter(word != "") |>
  filter(!str_detect(word, "[0-9]"))

# compute term frequencies
tf_clean <- RandJ_clean |>
  count(word, sort = TRUE)

# identify the most frequently occurring word in the text
tf_clean |> slice(1)
```
